Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-30 analysis/paper/hotspot-one-chromosome.Rmd
changed params to output_options

```{r, fig.height = ceiling(nlocal / 2)}
foo <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id)
p <- foo %>%
  ggplot() +
  geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = nonlocal_symbol), size = 0.1) +
  facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) +
  broman::karl_theme(strip.placement = "inside") +
  theme(legend.position = "none") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
) +
  xlab("Pleiotropy LOD") +
  ylab("Mediation LOD difference") +
  geom_text(aes(x = 1, y = 1, label = local_symbol), inherit.aes=FALSE)

>>>>

```{r, fig.height = ceiling(nlocal / 2)}
foo <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id)
p <- foo %>%
  ggplot() +
  geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = nonlocal_symbol), size = 0.1) +
  facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) +
  broman::karl_theme(strip.placement = "inside") +
  theme(legend.position = "none") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
) +
  xlab("Pleiotropy LOD") +
  ylab("Mediation LOD difference") +
  geom_text(aes(x = max(foo$pleiotropy_lod), y = 1, label = local_symbol), inherit.aes=FALSE)
